### 2015-12-29 text/ms.Rmd
Previous final edits + format switch

<!-- 
TODO
- justified or ragged?
- spell check American
-->

<!--notes:
http://onlinelibrary.wiley.com/journal/10.1111/(ISSN)1523-1739/homepage/ForAuthors.html

con bio: American spelling

Contributed Papers: 6000 words

Submit your cover page as a separate document. It should not be part of the manuscript itself. The cover page must include the title of the paper; a running head (short title of 40 or fewer characters); a list of 5-8 keywords; word count (all text from the first word of the Abstract through the last word of the Literature Cited but not including table or figure legends or the body of tables); authors' complete mailing addresses (including postal code) at the time the work was conducted and present addresses if different; name and complete address (including email) of the person to whom correspondence should be sent; and text of your acknowledgments section.

Contributed Papers, Research Notes, and Conservation Practice and Policy papers should contain the following sections in the following order: Abstract, Introduction, Methods, Results, Discussion, Supporting Information paragraph (if there are online appendices), Literature Cited, tables, figure legends, and figures. Do not combine sections (e.g., Results and Discussion). The Acknowledgments section will be added to the body of the paper after the manuscript has been accepted. Do not number section headings or subheadings. Do not include a Conclusion section (conclusions are part of the Discussion).

You may have color figures in the online version and gray-scale figures in print. However, reference to color cannot be made in the figure legend or in the text, and elements in the gray-scale version must be distinguishable. Supply separate files for color and gray-scale figures.

-->

@@

\noindent
Sean C. Anderson^1\*^, 
Andrew B. Cooper^1^,
Olaf P. Jensen^2^, 
C\'{o}il\'{i}n Minto^3^, 
James T. Thorson^4^,
Jessica C. Walsh^1^,
Jamie Afflerbach^5^, 
Mark Dickey-Collas^6,7^, 
Kristin M. Kleisner^8^, 
Catherine Longo^5^, 
Giacomo Chato Osio^9^, 
Daniel Ovando^10^, 
Iago Mosqueira^9^,
Andrew A. Rosenberg^11^, 
Elizabeth R. Selig^12^

@@

\noindent
^3^Galway-Mayo Institute of Technology, 
Marine and Freshwater Research Centre, Galway, 00000, Ireland

\noindent
^4^ Fisheries Resource Analysis and Monitoring Division, Northwest Fisheries Science Center, National Marine Fisheries Service, NOAA, Seattle, WA 98112

\noindent
^5^National Marine Fisheries Service, National Oceanographic and Atmospheric
Administration, Northeast Fisheries Science Center, Ecosystem Assessment
Program, 166 Water St., Woods Hole, MA, 02543, USA

@@

\noindent
^8^National Center for Ecological Analysis and Synthesis, University of
California Santa Barbara, 735 State Street, Suite 300, Santa Barbara, CA 93103,
USA

\noindent
^9^European Commission, Joint Research Centre, Institute for the Protection and
Security of the Citizen, Maritime Affairs Unit G03, Via E. Fermi 2749, 21027
Ispra (VA), Italy

\noindent
^10^University of California Santa Barbara, 
Bren School of Environmental Science and Management, 
Santa Barbara, CA, 93106-5131, USA

\noindent
^11^Union of Concerned Scientists, Cambridge, MA, USA

\noindent
^12^Conservation International, Arlington, VA, USA

@@

\bigskip
\noindent 
Keywords: data-limited fisheries, ensemble methods, multi-model averaging, population dynamics, sustainable resource management

\bigskip
\noindent 
Word count: TODO

\bigskip
<!--Place the acknowledgment paragraph on the cover page of your manuscript.
(Reviewers are not provided with a cover page.) Do not spell out first (given)
names. Provide the first initial of the first name, even if the initial starts a
sentence. Do not use titles (e.g., Dr. or Professor). Refer to authors of the
manuscript by their initials only (e.g., “S.T.W. was supported by a grant from
the Torry Foundation.”).-->
\noindent
Acknowledgements: We thank members of Phase I of the working group 'INSERT NAME HERE' who
contributed to developing the data-limited methods and simulations used in our
analysis.
We thank J.A. Hutchings for helpful discussions on ensemble methods for
assessing population status.
We thank the Gordon and Betty Moore Foundation for funding of the working group
'INSERT NAME HERE'.
'INSERT OTHER REQUIRED FUNDING ACKNOWLEDGEMENTS HERE'

\clearpage

\begin{LARGE}
\noindent
Improving estimates of population status and trend with superensemble models
\end{LARGE}

<!--up to 300 words-->

@@

\bigskip
<!--Include on the cover page five to eight words or phrases that will be useful for indexing and literature searches. Do not use words in the title as keywords, and avoid general terms such as conservation.-->

@@

Whereas averages or weighted averages may improve predictions over any single model, they may not optimally leverage available data. The best prediction does not necessarily lie in the middle of multiple model predictions, some models may perform better than others in certain conditions, and the covariance between models may contain information that can improve predictive accuracy. We can exploit these characteristics by using the predictions from a group of models as inputs into a separate statistical model. This technique, sometimes called superensemble modelling [@krishnamurti1999], is common in climate and weather forecasting [e.g. @yun2005; @mote2015]. The superensemble is fit to some training dataset where outcomes are well known and used to predict on a dataset of interest. For example, @krishnamurti1999 combined predictions of wind and precipitation in Asian monsoons via a superensemble regression fit to observed data. Their superensemble was considerably more accurate than any individual prediction or weighted average of predictions.

In fisheries science, the commonly used operational model for determining status and trend of exploited fish populations are stock assessments, i.e., population models coupled to an observation model, that incorporate all appropriate data (e.g. catches, size and age distributions, surveys, and tagging information) to quantify values such as the biomass of a stock that can produce maximum sustainable yield ($B/B_\mathrm{MSY}$) [@hilborn1992]. However, the broad range of data required to conduct these stock assessments are not available for the majority of fish populations, including those of conservation concern and of economic interest to fisheries [@fao2014]. Therefore, a number of models have been proposed to assess $B/B_\mathrm{MSY}$ based on the limited data available for the majority of fish stocks: (1) a time series of the total biomass of catch and (2) a basic understanding of population productivity [e.g. @vasconcellos2005; @martell2013]. Recently, @rosenberg2014 investigated the performance of four data-limited models through a large-scale simulation experiment. The four models frequently disagreed about population status, no one model had strong performance across all fish stocks, and some models performed better than others depending on circumstances (e.g. Fig. \ref{motivate}).

Here, we estimate population status and trend of exploited fish populations using ensembles and superensembles (collectively 'ensemble methods') of these four data-limited models. We apply four ensemble-method approaches of increasing complexity to both simulated and real-world fish stocks and compare their predictive performance against each other and against individual model productions.

@@

We first developed and tested ensemble methods on a fully factorial simulated dataset [@rosenberg2014] with known status. These published simulated data included the following scenarios: three fish life histories: small pelagic, demersal, and large pelagic; three levels of initial biomass depletion compared to carrying capacity: biomass at 100%, 70%, and 40% of carrying capacity; and four exploitation settings: (1) a constant exploitation rate, (2) an exploitation rate coupled with biomass to mimic an open-access single-species fishery, (3) a scenario where exploitation rate increased continuously, and (4) a 'roller-coaster' scenario where the exploitation rate increased and then decreased. Process noise (recruitment variability; i.e. unexplained variability in population dynamics) was introduced to the models at two magnitudes in log space, $N(0, 0.2^2)$ and $N(0, 0.6^2)$, and was either uncorrelated or had a first-order autoregressive correlation of $0.6$. The simulation also included a scenario with $N(0, 0.2^2)$ measurement error around log(catch) and one scenario without measurement error.

@rosenberg2014 ran ten iterations for each combination of factors adding stochastic draws of recruitment and catch-recording variability each time to generate a total of 5760 stocks. The simulation models were built in the package `FLR` [@kell2007, <http://flr-project.org>] for the statistical software \textsf{R} [@r2015]. Code to generate the simulations is available at <https://github.com/datalimited/stocksims>.

We also tested our ensemble methods on the RAM Legacy Stock Assessment Database [@ricard2012] --- a compilation of stock-assessment output from hundreds of exploited marine populations around the world. Our analysis of the stock-assessment database was based on version TODO; after removing stocks for which the models described below did not converge (121), this database included `r ram_stocks_n` stocks.

@@

We fit four individual data-limited models to estimate $B/B_\mathrm{MSY}$. Three of the models are mechanistic and based generally on Schaefer (logistic) biomass dynamics [@schaefer1954] of the form

@@

For all superensembles, we used the mean or slope of $B/B_\mathrm{MSY}$ as the response and the predictions from the individual models, and the spectral values, as the predictors. For superensemble models of mean $B/B_\mathrm{MSY}$ --- a ratio bounded at zero --- we fit the models in log space and exponentiated the predictions. For the estimates of $B/B_\mathrm{MSY}$ slope, which are not bounded at zero, we fit superensemble models on the natural untransformed scale.

We compared an ensemble average and three superensembles of varying complexity: a linear model with two-way interactions, a random forest, and a boosted regression tree. We fit the linear model superensemble with all second-order interactions. Our two machine learning superensemble models, a random forest and a boosted regression tree, were based on regression trees. Regression trees sequentially determine what value of a predictor best splits the response data into two 'branches' based on a specified loss function [@breiman1984]. In random forests, a series of regression trees are built on a random subset of the data and random subset of the covariates of the model [@breiman2001]. In generalized boosted models (GBMs), each subsequent model is fit to the residuals from the previous model; data points that are fit poorly in a given model are given more weight in the next model [@elith2008]. Random forests and GBMs can provide strong predictive performance and fit highly non-linear relationships [@elith2008; @hastie2009]. We fit random forest models with the `randomForest` package [@liaw2002] for \textsf{R} with the default argument values. We fit boosted regression tree models with the `gbm` package [@ridgeway2015] for \textsf{R}. Based on initial tuning with the **caret** \textsf{R} package [@caret2008], we chose to fit GBMs with 2000 trees, an interaction depth of $6$, a learning rate (shrinkage parameter) of $0.01$, and all other arguments at their default values.

@@

A critical component to predictive modelling is to evaluate the performance of a model on new data [@hastie2009]. We used repeated three-fold cross validation to test predictive performance: we randomly divided the dataset into three sets, built superensemble models on two-thirds of the data, and evaluated predictive performance on the remaining third. We repeated this across each of the three splits and then repeated the whole procedure 50 times to account for bias that may result from any one set of validation splits. In the simulated dataset, there were 10 replicates of each unique combination of simulation parameters that differed only in stochastic variability. Since the dynamics of these populations were often similar, we grouped these stocks in the cross-validation process into either the training or testing split. When applied to the RAM Legacy Stock Assessment database, we used superensembles trained on the entire simulation dataset. However, since mPRM is built on the same stock-assessment database, we refit mPRM on each training split.

Predictive performance can be evaluated with metrics that represent a variety of modelling goals. For continuous response variables such as the mean and slope of population status, performance metrics often measure some form of bias, precision, accuracy (a combination of bias and precision), or the ability to correctly rank or correlate across populations [e.g. @walther2005]. Here, we measure proportional error, defined as $(\hat{b} - b)/\abs{b}$, where $\hat{b}$ and $b$ represent estimated and 'true' (or stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median proportional error to measure bias, median absolute proportional error to measure accuracy, and Spearman's rank-order correlation between predicted and 'true' values to measure the ability to correctly rank populations. When cross-validating against the RAM Legacy Stock Assessment database, we treated the estimates from these data-rich stock assessments as known without error. Thus, any error in the stock-assessment estimates of the mean or slope of $B/B_\mathrm{MSY}$ also contributes to our estimates of prediction error for each of the four data-limited models and the ensembles. We measured the ability for each model to correctly place stocks into categories of above or below $B/B_\mathrm{MSY} = 0.5$ at any decision threshold by plotting receiver operating characteristic curves; a threshold of $B/B_\mathrm{MSY} = 0.5$ is used to classify a stock as overfished in Australia and the United States [@daff2007; @hilborn2010]. Code to reproduce our analysis is available at <https://github.com/datalimited/ensembles> (TODO: make public).

@@

Applied to the simulated dataset of known stock status, the individual models had variable success at recovering the mean (status) and slope (trend) of $B/B_\mathrm{MSY}$ in the last five years. All models exhibited a high degree of scatter around the one-to-one line of perfect status prediction (Fig. \ref{hexagon}). In contrast to the known unimodal distribution of status, CMSY exhibited bimodal predictions (Fig. \ref{hexagon}a), but had the best rank-order correlation and accuracy scores (Fig. \ref{performance}a). COM-SIR and SSCOM both correctly identified a number of stocks with low status, but frequently predicted a high status when status was in fact low (Fig. \ref{hexagon}b, c). mPRM had relatively poor ability to predict status for the simulated dataset (Fig. \ref{hexagon}d). There was generally little correlation between true and predicted trend for any of the individual models (rank-order correlation = `r range_slope_corr_non_sscom`) with the exception of SSCOM (correlation = `r slope_corr_sscom`; Figs \ref{scatter-sim-slope}a--d).

@@

Combining predictions from multiple models via superensemble methods is also broadly useful in other subfields of ecology and fisheries science. Predictions about extinction risk are widely used at the national (e.g. the US Endangered Species Act and the Canadian Species at Risk Act) and international [e.g. the IUCN Red List, @iucn2015] levels. These risk assessments generally involve fitting regression models to outcomes for individual species along with predictors of extinction risk [e.g. @anderson2011a; @pinsky2011], or population dynamics models to data for individual species [e.g. @dfo2010]. Both types of models are prone to error caused by model-misspecification and therefore results are sensitive to decisions about model structure [@brooks2015]. Although there are options to account for potential model-misspecification in determination of species risk [e.g. coefficient averaging, @burnham2002; generalized modeling, @yeakel2011; or semi-parametric methods, @thorson2014], ensemble methods are a relatively simple way to combine predictions in a transparent manner. Beyond estimates of status and trend, ensemble methods could be used to increase the robustness of spatial predictions when designing networks of protected areas [@rassweiler2014], to forecast potential spatial shifts in species distribution given climate impacts [@harsch2014], or to evaluate the effect of conservation management actions when experimental or observational data are limited [@walsh2012].

>>>>

<!--
 The full title of the paper, with two alternatives. Keep titles short and simple.
• The full names of all authors.
• The name(s) and address(es) of the institution(s) at which the work was carried out. If the present address of any author is different from the above, give it as a footnote.
• The name, address, telephone, fax and e-mail contacts of the author to whom all correspondence and proofs should be sent.
• A suggested running title of not more than 40 characters, including spaces.
-->

@@

\noindent
Sean C. Anderson^1\*^, 
Andrew B. Cooper^1^,
Olaf P. Jensen^2^, 
C\'{o}il\'{i}n Minto^3^, 
James T. Thorson^4^,
Jessica C. Walsh^1^,
Jamie Afflerbach^5^, 
Mark Dickey-Collas^6,7^, 
Kristin M. Kleisner^8^, 
Catherine Longo^9^, 
Giacomo Chato Osio^10^, 
Daniel Ovando^11^, 
Iago Mosqueira^10^,
Andrew A. Rosenberg^12^, 
Elizabeth R. Selig^13^

@@

\noindent
^3^Marine and Freshwater Research Centre, Galway-Mayo Institute of Technology, 
Galway, 00000, Ireland

\noindent
^4^Fisheries Resource Analysis and Monitoring Division, Northwest Fisheries Science Center, National Marine Fisheries Service, National Oceanographic and Atmospheric Administration, 2725 Montlake Boulevard E., Seattle, WA, 98112, USA

\noindent
^5^National Center for Ecological Analysis and Synthesis, University of
California Santa Barbara, 735 State Street, Suite 300, Santa Barbara, CA, 93103,
USA

@@

\noindent
^8^Ecosystem Assessment Program, Northeast Fisheries Science Center, National Marine Fisheries Service, National Oceanographic and Atmospheric Administration, 166 Water St., Woods Hole, MA, 02543, USA

\noindent
^9^Marine Stewarship Council, Marine House, 1 Snow Hill, London, EC1A 2DH, United Kingdom

\noindent
^10^European Commission, Joint Research Centre, Institute for the Protection and
Security of the Citizen, Maritime Affairs Unit G03, Via E. Fermi 2749, 21027
Ispra (VA), Italy

\noindent
^11^Bren School of Environmental Science and Management, 
University of California Santa Barbara, 
Santa Barbara, CA, 93106-5131, USA

\noindent
^12^Union of Concerned Scientists, Cambridge, MA, USA

\noindent
^13^Conservation International, Arlington, VA, USA

@@

\clearpage
<!--up to 250 words-->

@@

\noindent 
Keywords: data-limited fisheries, ensemble methods, multi-model averaging, population dynamics, sustainable resource management

\tableofcontents

@@

Whereas averages or weighted averages may improve predictions over any single model, they may not optimally leverage available data. The best prediction does not necessarily lie in the middle of multiple model predictions, some models may perform better than others in certain conditions, and the covariance between models may contain information that can improve predictive accuracy. We can exploit these characteristics by using the predictions from a group of models as inputs into a separate statistical model. This technique, sometimes called superensemble modelling [@krishnamurti1999], is common in climate and weather forecasting [e.g. @yun2005; @mote2015]. The superensemble is fit to a training dataset where outcomes are well known and used to predict on a dataset of interest (Fig. \ref{didactic}). For example, @krishnamurti1999 combined predictions of wind and precipitation in Asian monsoons via a superensemble regression fit to observed data. Their superensemble was considerably more accurate than any individual prediction or weighted average of predictions.

In fisheries science, the commonly used operational models for determining status and trend of exploited fish populations are stock assessments, i.e., population models coupled to an observation model, that incorporate all appropriate data (e.g. catches, size and age distributions, surveys, and tagging information) to quantify values such as the biomass of a stock that can produce maximum sustainable yield ($B/B_\mathrm{MSY}$) [@hilborn1992]. However, the broad range of data required to conduct these stock assessments are not available for the majority of fish populations, including those of conservation concern and of economic interest to fisheries [@fao2014]. Therefore, a number of models have been proposed to assess $B/B_\mathrm{MSY}$ based on the limited data available for the majority of fish stocks: (1) a time series of the total biomass of catch and (2) a basic understanding of population productivity [e.g. @vasconcellos2005; @martell2013]. Recently, @rosenberg2014 investigated the performance of four data-limited models through a large-scale simulation experiment. Three of these models are based on Schaefer (logistic) biomass dynamics and one is an empirical model fitted to more data-rich stock assessment output. The four models frequently disagreed about population status, no one model had strong performance across all fish stocks, and some models performed better than others depending on circumstances (e.g. Fig. \ref{motivate}).

Here, we estimate population status and trend of exploited fish populations using ensembles and superensembles (collectively 'ensemble methods') of these four data-limited models. We apply four ensemble-method approaches of increasing complexity to both simulated and real-world fish stocks and compare their predictive performance against each other and the individual models.

<!--
 TODO: It might be good to throw in a single sentence here describing the 4 models, or at least listing them and maybe a couple key differences among them.-->

@@

We first developed and tested ensemble methods on a fully factorial simulated dataset [@rosenberg2014] with known status. These published simulated data included the following scenarios: three fish life histories: small pelagic, demersal, and large pelagic; three levels of initial biomass depletion compared to carrying capacity: biomass at 100%, 70%, and 40% of carrying capacity; and four exploitation settings: (1) a constant exploitation rate, (2) an exploitation rate coupled with biomass to mimic an open-access single-species fishery, (3) a scenario where exploitation rate increased continuously, and (4) a 'roller-coaster' scenario where the exploitation rate increased and then decreased. Process noise (recruitment variability; i.e. unexplained variability in population dynamics) was introduced to the models at two magnitudes in log space, $N(0, 0.2^2)$ and $N(0, 0.6^2)$, and was either uncorrelated through time or had a first-order autoregressive correlation of $0.6$. The simulation also included a scenario with $N(0, 0.2^2)$ measurement error around log(catch) and one scenario without measurement error.
@rosenberg2014 ran ten iterations for each combination of factors adding stochastic draws of recruitment and catch-recording variability each time to generate a total of 5760 stocks.

<!--TODO add back when identity public: The simulation models were built in the package `FLR` [@kell2007, <http://flr-project.org>] for the statistical software \textsf{R} [@r2015]. -->
<!--Code to generate the simulations is available at <https://github.com/iagomosqueira/stockStatusFAO>.-->

We also tested our ensemble methods on the RAM Legacy Stock Assessment Database [@ricard2012] --- a compilation of stock-assessment output from hundreds of exploited marine populations around the world. Our analysis of the stock-assessment database was based on version 2.5; after removing stocks for which at least one of the individual models described below did not converge (121), this database included `r ram_stocks_n` stocks.

@@

We fit four individual data-limited models to estimate $B/B_\mathrm{MSY}$. Three of the models are mechanistic and based generally on Schaefer biomass dynamics [@schaefer1954] of the form

@@

We used the mean or slope of $B/B_\mathrm{MSY}$ as the response and the predictions from the individual models, and the spectral values, as predictors in our superensemble models. When modelling mean $B/B_\mathrm{MSY}$ --- a ratio bounded at zero --- we fit the superensemble models in log space and exponentiated the predictions. For the estimates of $B/B_\mathrm{MSY}$ slope, which are not bounded at zero, we fit superensemble models on the natural untransformed scale.

We compared an ensemble average and three superensembles of varying complexity: a linear model with two-way interactions, a random forest, and a boosted regression tree. We fit the linear model superensemble with all second-order interactions. Our two machine learning superensemble models, a random forest and a boosted regression tree, were based on regression trees. Regression trees sequentially determine what value of a predictor best splits the response data into two 'branches' based on a loss function [@breiman1984]. In random forests, a series of regression trees are built on a random subset of the data and random subset of the covariates of the model [@breiman2001]. In generalized boosted models (GBMs), each subsequent model is fit to the residuals from the previous model; data points that are fit poorly in a given model are given more weight in the next model [@elith2008]. Random forests and GBMs can provide strong predictive performance and fit highly non-linear relationships [@elith2008; @hastie2009]. We fit random forest models with the `randomForest` package [@liaw2002] for \textsf{R} with the default argument values. We fit boosted regression tree models with the `gbm` package [@ridgeway2015] for \textsf{R}. Based on initial tuning with the **caret** \textsf{R} package [@caret2008], we chose to fit GBMs with 2000 trees, an interaction depth of $6$, a learning rate (shrinkage parameter) of $0.01$, and all other arguments at their default values.

@@

A critical component to predictive modelling is to evaluate the performance of a model on new data [@hastie2009]. We used repeated three-fold cross validation to test predictive performance: we randomly divided the dataset into three sets, built superensemble models on two-thirds of the data, and evaluated predictive performance on the remaining third. We repeated this across each of the three splits and then repeated the whole procedure 50 times to account for bias that may result from any one set of validation splits. In the simulated dataset, there were 10 replicates of each unique combination of simulation parameters that differed only in stochastic variability. Since the dynamics of these populations were often similar, we grouped these stocks in the cross-validation process into either the training or testing split. We also validated the models using the RAM Legacy Stock Assessment database. In this case, we used superensembles trained on the entire simulation dataset. However, since mPRM is built on the same stock-assessment database, we applied three-fold cross-validation to the RAM Legacy Stock Assessment data underlying the mPRM model so that the dataset that mPRM was trained with (for the individual model and superensemble) was separate from the dataset it was tested on.

Predictive performance can be evaluated with metrics that represent a variety of modelling goals. For continuous response variables such as the mean and slope of population status, performance metrics often measure some form of bias, precision, accuracy (a combination of bias and precision), or the ability to correctly rank or correlate across populations [e.g. @walther2005]. Here, we measure proportional error, defined as $(\hat{b} - b)/\abs{b}$, where $\hat{b}$ and $b$ represent estimated and 'true' (or stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median proportional error to measure bias, median absolute proportional error to measure accuracy, and Spearman's rank-order correlation between predicted and 'true' values to measure the ability to correctly rank populations. When cross-validating against the RAM Legacy Stock Assessment database, we treated the estimates from these data-rich stock assessments as known without error. Thus, any error in the stock-assessment estimates of the mean or slope of $B/B_\mathrm{MSY}$ also contributes to our estimates of prediction error for each of the four data-limited models and the ensembles. We measured the ability for each model to correctly place stocks into categories of above or below $B/B_\mathrm{MSY} = 0.5$ at any decision threshold by plotting receiver operating characteristic curves; a threshold of $B/B_\mathrm{MSY} = 0.5$ is used to classify a stock as overfished in Australia and the United States [@daff2007; @hilborn2010]. Code to reproduce our analysis and an \textsf{R} package to fit the data-limited assessment models are available at <https://github.com/...> (*Private while in review*).

@@

Applied to the simulated dataset of known stock status, the individual models had variable success at recovering the mean (status) and slope (trend) of $B/B_\mathrm{MSY}$ in the last five years. All models exhibited a high degree of scatter around the one-to-one line of perfect status prediction (Fig. \ref{hexagon}). In contrast to the known unimodal distribution of status, CMSY exhibited bimodal predictions (Fig. \ref{hexagon}a), but had the best rank-order correlation and accuracy scores (Fig. \ref{performance}a). COM-SIR and SSCOM both correctly identified a number of stocks with low status, but frequently predicted a high status when status was in fact low (Fig. \ref{hexagon}b, c). mPRM had relatively poor ability to predict status for the simulated dataset (Fig. \ref{hexagon}d). There was generally little correlation between true and predicted recent trend in status for any of the individual models (rank-order correlation = `r range_slope_corr_non_sscom`) with the exception of SSCOM (correlation = `r slope_corr_sscom`; Figs \ref{scatter-sim-slope}a--d).

@@

Combining predictions from multiple models via superensemble methods is also broadly useful in other subfields of ecology and fisheries science. Predictions about extinction risk are widely used at the national (e.g. the US Endangered Species Act and the Canadian Species at Risk Act) and international [e.g. the IUCN Red List, @iucn2015] levels. These risk assessments generally involve fitting regression models to outcomes for individual species along with predictors of extinction risk [e.g. @anderson2011a; @pinsky2011], or population dynamics models to data for individual species [e.g. @dfo2010]. Both types of models are prone to error caused by model-misspecification and therefore results are sensitive to decisions about model structure [@brooks2015]. Although there are options to account for potential model-misspecification in determination of species risk [e.g. coefficient averaging, @burnham2002; generalized modeling, @yeakel2011; or semi-parametric methods, @thorson2014], ensemble methods are a relatively simple way to combine predictions in a transparent manner. Beyond estimates of status and trend, ensemble methods could be used, for example, to increase the robustness of spatial predictions when designing networks of protected areas [@rassweiler2014] or to forecast potential spatial shifts in species distribution given climate impacts [@harsch2014].

<!-- TODO put back when space: or to evaluate the effect of conservation management actions when experimental or observational data are limited [@walsh2012].-->

\noindent
**Acknowledgements**: We thank members of Phase I of the working group 'Developing new approaches to global stock status assessment and fishery production potential of the seas' who
contributed to developing the data-limited methods and simulations used in our
analysis.
We thank E. Jardim, F. Scott, and J.A. Hutchings for helpful comments during the development of this project, and R.D. Methot for comments on an earlier version of the manuscript.
We thank the Gordon and Betty Moore Foundation for funding the working group
'Applying data-limited stock status models and developing management guidance for unassessed fish stocks'.
